\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-11 notes/2loopNLSM.tex
Added some references

In this work, we will consider three different types of cubic representations, that we define below: 
\be
\stackrel{\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}}{\text{Fundamental}}\qquad\qquad \stackrel{\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}}{\text{Bifundamental}}\qquad\qquad \stackrel{\Acubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue}}{\text{Adjoint}}
\ee
In this review, we will present examples of this distinct kinematic representations that have appeared in the literature. Though from the get go, we stress that in this work we are interested in identifying the analog of adjoint representations of the kinematic numerators; those for which all legs are equally preferrenced by the functional dressing. The only non-trivial $S$-matrix in the literature that exhibits this property to all-loop order, is that of Zakharov-Mikhailov theory \citepls{}. We will briefly review the perturbative construction of this theory below.

@@

While introducing succesively higher spiin states to the NMHV lagrangian constructed in \citepls{} could in principle work at tree level, we will see that it is not consiisntent with what we find at general loop order. We will comment on this in \sect{}. For now, we will study how to construct one-loop integrands consistent with the color-kinematics by isolating the cubic sector of the state sum above. This is easily understood in terms of a polarization decomposition introduced by one of the authors \citepls{} that decomposes vector amplitudes in terms of building blocks that preserve partial amplitude relations. 

@@

Describe how different orders in $\varepsilon_i\varepsilon_j$ in pure Yang-Mills captures different cubic and contact sectors of the theory. All the $D$-dimensional Lagnrangians above can be understood as selecting specific on shell states to isolate the cubic sector of Yang-Mills at a given loop order. Start with reducible amplitude block decomp from Ref. \citepls{}:

@@

At this point color-kinematics duality has been satisfied, so the double copy will proceed without issue.
However, the plethora of generalized gauge freedom parameters leaves the option for enforcing additional aesthetic constraints.
$\mathcal{N}=4$ SYM provides several hints for further conditions to impose on the ansatz.
For example, for maximally supersymmetric gauge theory it is possible to enforce the no triangle hypothesis, manifest loop power counting, and, at least for 4pt and up to four loops, strip off a factor of $st A_\text{tree}$ from the integrand (I'm not sure I know all of the papers to cite here).
For the NLSM integrand it is desirable to make color-kinematics duality as manifest as possible.
One hope would be to factor out some piece of the 1-loop numerator since this at least manifests antisymmetry for the vertices involving external legs.
However, a more fruitful direction is to match onto the one known theory with pion power counting that manifests color-kinematics duality to all loop order, namely, Zakharov-Mikhailov theory \citepls{Original ZM paper, ZM CK paper}.

@@

It is tempting to try to match the pion 4pt 2-loop integrand to ZM on the cuts, but given that the cuts only probe the on-shell 4pt amplitude, which is either subtle or vanishes for ZM, it is better to compare the off-shell numerators directly.
As local functions, the numerators never suffer from any of the subtleties of on-shell 2D kinematics.
Since the physical cuts are difficult to compare, ZM theory is being used here simply as a tool to eliminate generalized gauge freedom; ZM theory has the right power counting and kinematic structure in 2D to compare against.
Since ZM theory is only being used for the kinematical structure of its numerators, it is natural to introduce a proportionality constant $z$ between the NLSM and ZM numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.
The parameter $z$, which would normally be fixed on cuts, effectively encodes the discrepancy between the coupling constants of the two theories.\footnote{Floating the proportionality parameter $z$ is also motivated because ZM is believed to be quantum mechanically different from NLSM even though they are dual classically \citepls{Nappi}.}
This introduces an extra degree of freedom into the problem.
Mechanically, the pion numerator is matched to ZM by first taking every possible assignment of right and left movers for the external particles and then restricting the pion numerator to 2D.
The loop momenta are restricted to 2D but left off-shell.
After performing the 2D matching, there are only 365 parameters of generalized gauge freedom.

@@

\section{Conclusions and Outlook}
\subsection{All-loop No-Go Theorem}
This could be a section about our expectations for all-loop construction requiring non-local color-dual integrands. Lay out counterfactual proof, i,e. define the following statement:
\be
 Q_L=\textit{``the $L$-loop numerator is polynomial and color-dual"}. 
\ee
Then it is clear that if the kinematic numerator is polynomial and color-dual, evaluating it in kinematic regions where the internal legs are on-shell won't disrupt the kinematic algrebraic relations, and it must still be polynomial. Thus we find:
\be
Q_L \Rightarrow Q_{L-1}
\ee
Or equivalently,
\be
\text{not }Q_{L-1}\Rightarrow \text{not }Q_L
\ee
We have found that the two-loop integrand for Yang-Mills cannot be constructed from a color-dual polynomial kinematic numerator. Thus, if a color-dual representation exists at all-loop order for Yang-Mills it must be a rational function of kinematics. 
\subsection{Future Directions}\label{sec:Discussion}
\paragraph{Acknowledgments} The authors would like to thank ... for insightful conversations, related collaboration, and encouragement throughout the completion of this work. This work was supported by the DOE under contract DE-SC0015910 and by the Alfred P. Sloan Foundation. N.H.P. additionally acknowledges the Northwestern University Amplitudes and Insight group, the Department of Physics and Astronomy, and Weinberg College for their generous support.

Figures made with TikZ-Feynman [1601.05437]

>>>>

In this work, we will consider three different types of cubic representations, that we define below: 
\be
\stackrel{\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}}{\text{Fundamental}}\qquad\qquad \stackrel{\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}}{\text{Bifundamental}}\qquad\qquad \stackrel{\Acubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue}}{\text{Adjoint}}
\ee
In this review, we will present examples of this distinct kinematic representations that have appeared in the literature. Though from the get go, we stress that in this work we are interested in identifying the analog of adjoint representations of the kinematic numerators; those for which all legs are equally preferrenced by the functional dressing. The only non-trivial $S$-matrix in the literature that exhibits this property to all-loop order, is that of Zakharov-Mikhailov theory \cite{Zakharov:1973pp, Cheung:2022mix}. We will briefly review the perturbative construction of this theory below.

@@

While introducing succesively higher spin states to the NMHV Lagrangian constructed in \cite{Ben-Shahar:2022ixa} could in principle work at tree level, we will see that it is not consistent with what we find at general loop order. We will comment on this in \sect{}. For now, we will study how to construct one-loop integrands consistent with the color-kinematics by isolating the cubic sector of the state sum above. This is easily understood in terms of a polarization decomposition introduced by one of the authors \cite{Pavao:2022kog} that decomposes vector amplitudes in terms of building blocks that preserve partial amplitude relations. 

@@

Describe how different orders in $\varepsilon_i\varepsilon_j$ in pure Yang-Mills captures different cubic and contact sectors of the theory. All the $D$-dimensional Lagnrangians above can be understood as selecting specific on shell states to isolate the cubic sector of Yang-Mills at a given loop order. Start with reducible amplitude block decomp from Ref. \cite{Pavao:2022kog}:

@@

At this point color-kinematics duality has been satisfied, so the double copy will proceed without issue.
However, the plethora of generalized gauge freedom parameters leaves the option for enforcing additional aesthetic constraints.
$\mathcal{N}=4$ SYM provides several hints for further conditions to impose on the ansatz.
For example, for maximally supersymmetric gauge theory it is possible to enforce the no triangle hypothesis, manifest loop power counting, and, at least for 4pt and up to four loops, strip off a factor of $st A_\text{tree}$ from the integrand (I'm not sure I know all of the papers to cite here).
For the NLSM integrand it is desirable to make color-kinematics duality as manifest as possible.
One hope would be to factor out some piece of the 1-loop numerator since this at least manifests antisymmetry for the vertices involving external legs.
However, a more fruitful direction is to match onto the one known theory with pion power counting that manifests color-kinematics duality to all loop order, namely, Zakharov-Mikhailov theory \cite{Zakharov:1973pp, Cheung:2022mix}.

@@

It is tempting to try to match the pion 4pt 2-loop integrand to ZM on the cuts, but given that the cuts only probe the on-shell 4pt amplitude, which is either subtle or vanishes for ZM, it is better to compare the off-shell numerators directly.
As local functions, the numerators never suffer from any of the subtleties of on-shell 2D kinematics.
Since the physical cuts are difficult to compare, ZM theory is being used here simply as a tool to eliminate generalized gauge freedom; ZM theory has the right power counting and kinematic structure in 2D to compare against.
Since ZM theory is only being used for the kinematical structure of its numerators, it is natural to introduce a proportionality constant $z$ between the NLSM and ZM numerators $n_\text{NLSM} \vert_{2D} = z ~ n_\text{ZM}$.
The parameter $z$, which would normally be fixed on cuts, effectively encodes the discrepancy between the coupling constants of the two theories.\footnote{Floating the proportionality parameter $z$ is also motivated because ZM is believed to be quantum mechanically different from NLSM even though they are dual classically \cite{Nappi:1979ig}.}
This introduces an extra degree of freedom into the problem.
Mechanically, the pion numerator is matched to ZM by first taking every possible assignment of right and left movers for the external particles and then restricting the pion numerator to 2D.
The loop momenta are restricted to 2D but left off-shell.
After performing the 2D matching, there are only 365 parameters of generalized gauge freedom.

@@

\section{Conclusions and Outlook}
\subsection{All-loop No-Go Theorem}
This could be a section about our expectations for all-loop construction requiring non-local color-dual integrands. Lay out counterfactual proof, i,e. define the following statement:
\be
 Q_L=\textit{``the $L$-loop numerator is polynomial and color-dual"}. 
\ee
Then it is clear that if the kinematic numerator is polynomial and color-dual, evaluating it in kinematic regions where the internal legs are on-shell won't disrupt the kinematic algrebraic relations, and it must still be polynomial. Thus we find:
\be
Q_L \Rightarrow Q_{L-1}
\ee
Or equivalently,
\be
\text{not }Q_{L-1}\Rightarrow \text{not }Q_L
\ee
We have found that the two-loop integrand for Yang-Mills cannot be constructed from a color-dual polynomial kinematic numerator. Thus, if a color-dual representation exists at all-loop order for Yang-Mills it must be a rational function of kinematics. 
\subsection{Future Directions}\label{sec:Discussion}
\paragraph{Acknowledgments} The authors would like to thank ... for insightful conversations, related collaboration, and encouragement throughout the completion of this work. This work was supported by the DOE under contract DE-SC0015910 and by the Alfred P. Sloan Foundation. N.H.P. additionally acknowledges the Northwestern University Amplitudes and Insight group, the Department of Physics and Astronomy, and Weinberg College for their generous support.
Feynman diagrams were typeset using TikZ-Feynman \cite{Ellis:2016jkw}.
